### 2024-06-25 manuscript.Rmd
fixed figure caption

```{r rstudioscreen1, fig.cap="Reproducibility report shown when a document is created for the first time and no reproducibility information is available yet."}
knitr::include_graphics("img/rstudio-screenshot-marker2.png")
```

>>>>

```{r rstudioscreen1, fig.cap="Automated testing of variables for reproducibility is initiated by using code chunks of type `reproducibleR` (see yellow highlight) instead of `R` as shown in this example R Markdown snippet. "}
knitr::include_graphics("img/rstudio-screenshot-marker2.png")
```
